How to estimate the redshift density distribution

### 2017-01-27 research/paper/draft.tex
small changes to abstract

This paper presents a novel approach to estimating the posterior distribution over $n(z)$ from a survey of galaxy photo-$z$ PDFs based upon a probabilistic graphical model.  We present the Cosmological Hierarchical Inference with Probabilistic Photometric Redshifts (CHIPPR) code implementing this technique, as well as its validation on mock data and testing on a subset of BOSS DR10.  The code and method are easily extensible to other one-point statistics of redshift that are informative to galaxy evolution and large-scale structure.

>>>>

This paper presents a novel approach to estimating the posterior distribution over $n(z)$ from a survey of galaxy photo-$z$ PDFs based upon a probabilistic graphical model.  We present the Cosmological Hierarchical Inference with Probabilistic Photometric Redshifts (CHIPPR) code implementing this technique, as well as its validation on mock data and testing on a subset of BOSS DR10.  CHIPPR yields a more comprehensive and accurate characterization of $n(z)$ than traditional procedures.  The code is easily extensible to other one-point statistics of redshift that are informative to galaxy evolution and large-scale structure.
